### 2017-11-04 monograph/thesis/chapters/beautifiers.tex
Fixed spaces between chapters on the table of contents (toc) and
chapters titles.
Removed copied text on good_practices.tex and let only the
reference to the original text.
Fixed Sublime Text LatexTools (Log parsing issues. Disregard unless
something else is wrong.), issue:
(Log parsing issues. Disregard unless something else is wrong.)
https://github.com/SublimeText/LaTeXTools/issues/1216
Split the object_beautifier.tex The Problem section to other
related chapters.

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{Motivation}{Motivação}}

\begin{englishtext}

    \section{Application fields for code beautifiers}

    \citeonline{annotationAssistant},
    \citeonline{codePlagiarismDetection},
    \citeonline{softwarePortfolio},
    \citeonline{legacyAssets},
    \citeonline{massMaintenance},
    \citeonline{prettyPrinting},
    \citeonline{architectureFormatting},
    \citeonline{independentFramework},
    \citeonline{programIndentation},
    \citeonline{industrialApplication},
    \citeonline{toolsForProjectManagement},
    \citeonline{codeClassification},
    \citeonline{codeScanningPatterns},
    \citeonline{debuggingIntoExamples},
    \citeonline{programUnderstanding},
    \citeonline{documentingAndSharingKnowledge},
    \citeonline{autofoldingForSourceCode},
    \citeonline{learningSupportSystem},
    \citeonline{syntaxHighlightingInfluencing},
    \citeonline{improvingCodeReadability},
    \citeonline{howNovicesRead},
    \citeonline{theRoleOfMethodChains},
    \citeonline{codeComprehensionComparedToOO},
    \citeonline{enhancingLegacySoftwareSystemAnalysis},
    \citeonline{moldableCodeEditor},
    \citeonline{blindAndSightedProgrammers},

\end{englishtext}

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Source Code Beautifiers}

    Below there are some basic formatting rules for illustration:

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nosep,nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{bluebox}
    \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

    \section{For what is their use?}

    For now could not find any strong evidence or correlation about code
    comprehension and source code beautifying .

    \begin{citacao}
    % \setlength{\itemindent}{5pt}
    One of absolute worst, worst methods of teamicide for software developers is to engage
    in these kinds of passive-aggressive formatting wars. I know because I've been there.
    They destroy peer relationships, and depending on the type of formatting, can also damage
    your ability to effectively compare revisions in source control, which is really scary.
    I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
    leading by example, all right. Bad example. \cite{Atwood}
    \end{citacao}

    \begin{citacao}
    So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
    trivial issues of code layout is actually justified. Within reason of course -- when done
    openly, in a fair and concensus building way, and without stabbing your teammates in the
    face along the way. \cite{Atwood}
    \end{citacao}

    \section{Application Fields}

    \citeonline{annotationAssistant},
    \citeonline{codePlagiarismDetection},
    \citeonline{softwarePortfolio},
    \citeonline{legacyAssets},
    \citeonline{massMaintenance},
    \citeonline{prettyPrinting},
    \citeonline{architectureFormatting},
    \citeonline{independentFramework},
    \citeonline{programIndentation},
    \citeonline{industrialApplication},
    \citeonline{toolsForProjectManagement},
    \citeonline{codeClassification},
    \citeonline{codeScanningPatterns},
    \citeonline{debuggingIntoExamples},
    \citeonline{programUnderstanding},
    \citeonline{documentingAndSharingKnowledge},
    \citeonline{autofoldingForSourceCode},
    \citeonline{learningSupportSystem},
    \citeonline{syntaxHighlightingInfluencing},
    \citeonline{improvingCodeReadability},
    \citeonline{howNovicesRead},
    \citeonline{theRoleOfMethodChains},
    \citeonline{codeComprehensionComparedToOO},
    \citeonline{enhancingLegacySoftwareSystemAnalysis},
    \citeonline{moldableCodeEditor},
    \citeonline{blindAndSightedProgrammers},
    \citeonline{pushdownAutomata}

### 2017-11-04 monograph/thesis/chapters/introduction.tex
Fixed Sublime Text LatexTools (Log parsing issues. Disregard unless
something else is wrong.), issue:
(Log parsing issues. Disregard unless something else is wrong.)
https://github.com/SublimeText/LaTeXTools/issues/1216
Split the object_beautifier.tex The Problem section to other
related chapters.

\begin{englishtext}

@@

@@

    \section{Goals}

    \subsection{Specific Goals}

    \begin{enumerate}

        \item Establish relationships between good programming practices and efficiency in
        programming, in addition to a new tool to support programmers in order to
        automate the long and diverse programming process in teams of developers
        with different programming `best practices'.

        \item Define, determine and classify which one are good programming
        practices and perform an in-depth study on the good practices on visual
        layout area, also known as code `Beautifying'.

        \item The definition of a flow pattern of development allowing teams of
        developers with different programming best practices, to work without
        intervene with each other up to start wars of `best good practices'.

        \item Discourse on the variety of existing tools for the support of good
        programming practices, with a comparative analysis between them,
        determining their weaknesses and strengths.

@@

\end{englishtext}

% % Portuguese
% \lang{}{\input{chapters/introdução}}

>>>>

@@

    \begin{citacao}
    I'd say there are two main reasons to enforce a single code format in a project. First has
    to do with version control: with everybody formatting the code identically, all changes in
    the files are guaranteed to be meaningful. No more just adding or removing a space here or
    there, let alone reformatting an entire file as a `side effect' of actually changing just a
    line or two. \cite{Geukens}
    \end{citacao}

@@

    \section{Research Goals}

    \begin{enumerate}
        \item Establish relationships between good programming practices and efficiency in
              programming, in addition to a new tool to support programmers in order to
              automate the long and diverse programming process in teams of developers
              with different programming `best practices'.
        \item Define, determine and classify which one are good programming
              practices and perform an in-depth study on the good practices on visual
              layout area, also known as code `Beautifying'.
        \item The definition of a flow pattern of development allowing teams of
              developers with different programming best practices, to work without
              intervene with each other up to start wars of `best good practices'.
        \item Discourse on the variety of existing tools for the support of good
              programming practices, with a comparative analysis between them,
              determining their weaknesses and strengths.
    \end{enumerate}

@@

    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:

    \begin{enumerate}[leftmargin=*]
        \item There are many different tools, sometimes paid, and difficult to
              complete. \cite{universalCodeFormatter}

        \item Many programming languages exist, so always having Beautifier
              software for each of them is very laborious
              \cite{universalCodeFormatter}. But the approach to a Universal
              Beautifier proposed in this work, would allow easily new languages to be
              added, being completely different from previous ones, or alike. And in
              case of similarities between them, it is enough to reuse their
              configuration structures already implemented.

        \item Looking for a Beautifier for each one of them because programmers
              currently work daily with several of these languages, and they are not
              similar. So you need to configure several beautifiers to do the
              formatting. This is a problem because only a few beautifiers are more
              complete, and every time you need to make a change in the formatting
              style, you must manually propagate the same change over several
              different program configuration files, which is bad because it takes the
              user a lot of time to learn how to handle many different types of
              settings. \cite{Schweitzer}

        \item In the case of ideal Beautifier, a change in your styling is
              propagated to all languages. And if you want to leave some language out
              of it, you just need to remove it from the list on which the
              configuration block applies to, and `a)' leave it out so no change is
              applied to. Or `b)' create a new block including only the block within
              the desired settings.

% 1.2      Rascunho da Monografia para TCC1

% 1.2.1    * Introdução       Uma breve descrição dos objetivos e da
%            justificativa para realização do projeto. Uma breve explicação de
%            qual a necessidade e importância deste projeto no escopo da
%            Ciência da Computação. Os objetivo gerais e específicos buscados
%            após a conclusão e análise deste projeto.

% 1.2.2    * Bibliográfia     Fazer uma análise do estado da arte em relação
%          ao que existe hoje em dia de cunho científico, comentando sobre os
%          diversos trabalhos na área de beautifying.

% 1.2.3    * Classificações   Escrever sobre quais são os tipos possíveis de
%          beautifying. Quais são as técnicas mais eficientes, para quais
%          linguagens ele se aplicam.

% Cronograma:

% Id      Atividade                               Data início    Data fim
% 1.2.2.a Escrever sobre os Formatadores Atuais   31/07/2017     30/08/2017
% 1.2.2.b Escrever sobre as Pesquisas Atuais      01/09/2017     15/09/2017
% 1.2.3.a Escrever as Classes de Beautifying      16/09/2017     30/09/2017
% 1.2.3.b Escrever os Tipos de Beautifying        01/10/2017     30/10/2017
% 1.2.4.a Fazer a Revisão do Texto Escrito        31/10/2017     20/11/2017

### 2017-11-04 monograph/thesis/chapters/object_beautifier.tex
From motivation.tex, created new chapters beautifiers.tex,
good_practices.tex and renamed implementation.tex to
object_beautifier.tex
Fixed spaces between chapters on the table of contents (toc) and
chapters titles.
Fixed Sublime Text LatexTools (Log parsing issues. Disregard unless
something else is wrong.), issue:
(Log parsing issues. Disregard unless something else is wrong.)
https://github.com/SublimeText/LaTeXTools/issues/1216
Split the object_beautifier.tex The Problem section to other
related chapters.

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{Implementation}{Implementação}}\label{sec:implementation}

\begin{englishtext}

@@

    Below there are some basic formatting rules for illustration:

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nosep,nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{bluebox}
    \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:

        \item There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}

        \item Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.

        \item Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}

        \item In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.

        \item
        \begin{citacao}
        % \setlength{\itemindent}{5pt}
        One of absolute worst, worst methods of teamicide for software developers is to engage
        in these kinds of passive-aggressive formatting wars. I know because I've been there.
        They destroy peer relationships, and depending on the type of formatting, can also damage
        your ability to effectively compare revisions in source control, which is really scary.
        I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
        leading by example, all right. Bad example. \cite{Atwood}
        \end{citacao}

        \item
        \begin{citacao}
        So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
        trivial issues of code layout is actually justified. Within reason of course -- when done
        openly, in a fair and concensus building way, and without stabbing your teammates in the
        face along the way. \cite{Atwood}
        \end{citacao}

        \item
        \begin{citacao}
        I'd say there are two main reasons to enforce a single code format in a project. First has
        to do with version control: with everybody formatting the code identically, all changes in
        the files are guaranteed to be meaningful. No more just adding or removing a space here or
        there, let alone reformatting an entire file as a `side effect' of actually changing just a
        line or two. \cite{Geukens}
        \end{citacao}

@@

\end{englishtext}

% % Portuguese
% \lang{}{\input{chapters/implementação}}

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Object Beautifier}

    \section{Introduction}

@@

@@
